Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-02 manuscript.Rmd
Edits to intro

The cohesiveness and strength of social movements in the pre-Internet era could
be operationalized by the number of people turning out to protest and through
the political events that precipitated and resulted from social gatherings *en
masse*. The content of placards and protest signs provided the protest narrative
in their own words. Cohesive social movements were reflected in their cohesive
placards and posters. For example, the “I am a man” posters held by the men
involved in the 1968 sanitation workers' strike reflected their internal
cohesion and unified, goal-oriented movement [@Windsor2020].

@@

Disentangling the complicated relationship between mass online
mobilization---and social mobilization in person---continues to be relevant,
even as our modes of communication change. The political processes that
transpired during and after the Arab Spring are still in the process of being
understood. As Zeitzoff [-@zeitzoff2017social] recognizes, social media is
changing conflict, but the mechanisms and relationships by which it does so are
still being understood.

>>>>

The cohesiveness and strength of social movements in the pre-Internet era could
be operationalized by the number of people turning out to protest and through
the political events that precipitated and resulted from social gatherings *en
masse*. Cohesive social movements were reflected in their cohesive placards and
posters. For example, the “I am a man” posters held by the men involved in the
1968 sanitation workers' strike reflected their internal cohesion and unified,
goal-oriented movement [@Windsor2020].

@@

Disentangling the complicated relationship between mass online
mobilization---and social mobilization in person---continues to be relevant,
even as our modes of communication change. The political events that
transpired during and after the Arab Spring are still in the process of being
understood. As Zeitzoff [-@zeitzoff2017social] recognizes, social media is
changing conflict, but the mechanisms and relationships by which it does so are
still being understood.
